---
title: "Readme"
author: "Xi Zeng"
date: "2022-12-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the App

This is an app for data exploration and modelling as well as subsetting data for the raisin dataset from UCI machine learning repository,see <https://archive.ics.uci.edu/ml/datasets/Raisin+Dataset#> for more details.  

## Packages list needed to nun the App
[`shiny`](https://cran.r-project.org/web/packages/shiny/index.html)  
[`tidyverse`](https://www.tidyverse.org/)  
[`shinydashboard`](https://cran.r-project.org/web/packages/shinydashboard/index.html)  
[`DT`](https://www.rdocumentation.org/packages/DT/versions/0.16)  
[`readxl`](https://readxl.tidyverse.org/)  
[`tree`](https://www.rdocumentation.org/packages/tree/versions/1.0-42)  
[`randomForest`](https://www.rdocumentation.org/packages/randomForest/versions/4.7-1.1)  
[`caret`](https://topepo.github.io/caret/)  

# Code for Install Package Lists  
```{r, echo=TRUE, eval=FALSE}
install.packages(c("shiny", "tidyverse", "shinydashboard",
                   "DT", "readxl", "tree", "randomForest","caret"))

```

## Code for run the App  

```{r echo=TRUE, eval=FALSE}
shiny::runGitHub(repo = "ST558-FinalProject", username = "XiZeng929")
```

# Code to render README file  
```{r README, echo=TRUE, eval=FALSE}
rmarkdown::render("readme.Rmd", 
          output_format = "github_document",
          output_file = "README.md",
          output_options = list(
            html_preview = FALSE))